% Objectives
\section{Objectives}
\label{sec:objectives}
This special problem aims to develop a system that makes investing easier, 
more publicly available, data-driven, and more approachable by minimizing both the 
time required for stock price trend analysis, and potential financial risk 
by using DMD-LSTM and integrate Arnaud Legoux Moving Average Convergence-Divergence (ALMACD)
as a trading algorithm. More specifically, it aims to do following:
\begin{itemize}
  \item[(a)] Develop a system called alamSYS that can collect and process stock market data in order 
  to provide comprehensive stock position suggestions using Dynamic Mode - Long Short-Term Memory with 
  Arnaud Legoux Moving Average Convergence-Divergence integration. Specifically, this was done
  by creating the following:
    \begin{itemize}
      \item[1.] Develop a data preprocessor, referred to as alamPREPROCESSOR. 
      Which includes the following:
        \begin{itemize}
          \item[1.1] Data Collector Module (DCM) - collects the end-of-day historical data of a 
          stock from Mondays to Fridays. The data collected is then processed by the DPM.
          \item[1.2] Data Processor Module (DPM) - applies the deep learning model and 
          integrate the trading algorithm to the data. Finally, the processed data is given 
          to the DUM to be further processed.
          \item[1.3] Database Updater Module (DUM) - updates the database of the alamSYS
          with the new set of stocks to buy and sell for that specific trading day.
        \end{itemize}
      \item[2.] Develop a RESTful API, referred to as alamAPI, 
      using Python's FastAPI for handling the API endpoints.
      Specifically, the following API endpoints were developed:
        \begin{itemize}
            \item[2.1] Home – this API endpoint outputs a welcome message. 
            Which should inform the user that they have successfully connected to the alamAPI.
            \item[2.2]	Stocks to Buy – this API endpoint outputs a list of suggested 
            stocks to buy based from the current market price and the predicted price up-trend.
            \item[2.3] Stocks to Sell – this API endpoint outputs a list of suggested
            stocks to sell based from the current market price and the predicted price down-trend.
            \item[2.4]  Stocks Info - this API endpoint outputs a list of stocks included 
            in the alamSYS and their corresponding information.
            \item[2.5]  ML Model Info - this API endpoint outputs a list of the 
            Machine Learning Models used in the alamSYS and their corresponding information.
            \item[2.6] Stocks Risks Info - this API endpoint outputs a list 
            of the stocks included in the alamSYS and their corresponding 
            risks values based on value at risk (\%), volatility (\%), and drawdown (\%).
        \end{itemize}
      \item[3.] Develop a database called alamDB, that stores the results provided by the DPM and DUM,
      and other essential data such as stock information, deep learning model information,
      and stock risks information about the stock market that is needed to be provided.
    \end{itemize}

  \item[(b)] Develop a Stock Market Price Trend Forecasting 
  Deep Learning Models by utilizing the dynamic modes in DMD as an additional input 
  parameter to an LSTM model. Afterwards, integrate the forecasting with ALMACD as
  a trading algorithm and basis for entry and exit positions.

  \item[(c)] Finally, develop a mobile-based test application, which from hereon maybe referred to 
  as: alamAPP, to showcase the main functionalities of the developed RESTful API. 
  Specifically which stocks to buy and to sell for a given period of time.
\end{itemize}