\section{The Implications of alamSYS to the Society}
\label{sec:implications}
Based on the findings summary presented in the previous section, the 
combination of several key components, including the alamSYS, 
DMD-LSTM model with the optimized ALMACD, and mobile-based test application 
(alamAPP), has the potential to revolutionize the Philippine financial 
stock market.
\\

The alamSYS was discovered to be dependable, stable, and efficient, with 
quick response times and the ability to handle a huge number of queries. 
While, through cross-validation, the DMD-LSTM model performed within an acceptable 
error range and proved acceptable performance outside of its training data.
\\

Furthermore, the incorporation of optimized ALMACD confirms that all alamSYS 
suggestions generate positive returns, limiting potential risks and 
lowering potential losses. Also, the alamAPP illustrated how the alamSYS might 
be used with other internet-connected devices. Overall, it positions itself 
as an accessible stock market investment tool for all Filipinos, with the 
goal of supporting and empowering investors to make informed decisions 
and navigate the stock market confidently, even amid difficult market 
situations.
\\

To put it simply, the sociological implications of a system such as alamSYS 
have a substantial impact on the potential benefits it could offer to the 
stock market, individual investors or traders, and the Philippine economy 
as a whole. The system has the potential to drive economic growth by 
providing jobs and pushing market advances. The system could boost investor 
trust and involvement in the stock market by offering credible stock trading 
advice and limiting potential risks and losses, resulting in a more healthy 
and prosperous economy.
\\