\section{Summary of Findings}
\label{sec:sum_find}
The following is a summary of the key findings, in accordance with 
the objectives outlined in Chapter 2 of this special problem and 
building on the discussions of the results in Chapter 4.

\begin{itemize}
    \item[(a)] In connection to the development of the alamSYS:
        \begin{itemize}
            \item When idle, the alamSYS's average CPU and memory utilization 
            is 0.43\% and 525.29 MiB, respectively. Whereas the 
            alamPREPROCESSOR uses the least amount of CPU power, 
            it also uses the most memory due to the scheduling program being active.
            \item Both alamAPI and alamPREPROCESSOR use a small amount of CPU power when idle, 
            which is due to the low system requirements of their linux-based base images.
            \item The alamPREPROCESSOR was able to process 100 consecutive data collection 
            and processing, indicating a 100 times higher working capacity than expected.
            \item The alamPREPROCESSOR's average runtime is 48.30 seconds. Which have
            been affected by the internet connection speed of 52.98Mbps on average.
            \item It also uses an average of 20.03\% of the CPU power and 794.29 MiB of memory on load. 
            This means that the alamPREPROCESSOR can be used with low-end devices.
            \item When alamPREPROCESSOR is loaded, its CPU and memory utilization are 
            99.95\% and 60.62\% higher, respectively, than when it is idle.
            \item The average deployed API response time is 1.34 seconds, 
            which is within the acceptable range for avoiding user-perceived interruptions.
            \item The delay from the tunneling service accounts for 99.30\% of the response time, 
            and the actual response time of the alamAPI is only 0.009 seconds on average; and
            \item The average CPU power utilization of alamAPI and alamDB on load is 
            99.05\% and 76.24\% higher, respectively, than their idle CPU power 
            utilizations. This allows them to process 71,000 requests in about 
            an hour and 20 minutes. On a different note, onload memory utilization was 
            found to be lower than idle values, but this could simply be due to dips in 
            zero MiB memory utilization over time, as shown in Figure \ref{fig:memory_util_onload}.
        \end{itemize}
        Overall, the findings show that the alamSYS and its three major components 
        (alamPREPROCESSOR, alamAPI, and alamDB) were successfully developed and integrated. 
        Its idle and on-load performance were guaranteed to be dependable, stable, and efficient.
        \hfill \\

    \item[(b)] In connection to the development of DMD-LSTM Model, and ALMACD Trading Algorithm:
        \begin{itemize}
            \item The DMD-LSTM model with a window size of 5 outperformed the other eight 
            LSTM models that were trained and tested. 
            Where the MSE, RMSE, MAE, and MAPE values are 0.000037, 0.006106, 0.004175, and 0.000001,
            respectively.
            \item Cross-validation of the selected DMD-LSTM model reveals acceptable 
            performance outside of its training data.
            \item Up to ten days of consecutive predictions show that the DMD-LSTM model 
            still produces a range of acceptable MAPE scores. However, to avoid the possibility of 
            extrapolation problems affecting the predictions, the alamSYS only integrated up to 5 days of 
            successive predictions. The extrapolation problem on LSTM models were also demonstrated in the 
            studies by \citeA{s19183988}; and \citeA{rs15061529}.
            \item The integration of optimized ALMACD on top of the DMD-LSTM model ensures that the alamSYS 
            recommendations return positive yields for all stocks.
            \item The DMD-LSTM and ALMACD applications in alamSYS were tested in real-world trading for a total 
            of 10 trading days, outperforming the PSEI on cumulative return. Furthermore, the alamSYS is capable 
            of mitigating risk and reducing potential losses in its position due to its ability to react quickly 
            on potential price changes attributed to its 5 days in advance predictions and reactive ALMA parameters.
        \end{itemize}
        Overall, the combination of DMD-LSTM predictions and ALMACD as a trading algorithm ensures that the alamSYS 
        suggests stock positions that, in theory, yield the highest positive returns while mitigating potential risks 
        associated with market price volatility.
        \hfill \\

    \item[(c)] In connection to the development of the mobile-based test application. The mobile-based application 
    demonstrated the potential of the alamSYS with other external internet-connected devices, such as a smartphone device.
\end{itemize}