% Significance of the Study
\section{Significance of the Study}
\label{sec:significance}
The significance of this special problem lies in its potential to develop a 
system that will greatly benefit the stock market, individual investors, and 
the overall economy. The system's contributions to data-driven investing, 
financial protection and management, and economic development will provide 
a valuable resource for investors and help to promote financial stability and growth. 
Additionally, the development of publicly accessible data-driven investing tools 
will enable more Filipinos to participate in the market and take control of their 
own financial future. Overall, this study has the potential to make a meaningful 
impact on the stock market and the economy in the Philippines.
\hfill \\

Specifically, this study is significant for the following reasons:
\begin{itemize}
  \item[(a)] The development of the alamAPI will provide the 
  following benefits to the Filipino people:
  \subitem 1.	Access to simplified yet accurate information 
  – The proposed system will provide Filipino investors with fast, 
  accurate, and relevant information necessary for effective decision making 
  in the stock market. Using advanced machine learning classifiers, the system 
  will provide users with the two most important pieces of information: 
  which stocks to buy, and which stocks to sell. This simplified investing 
  model will help investors to make informed decisions and navigate the stock 
  market with confidence.
  \subitem 2.	Provide an application interface to facilitate data-driven 
  and wise market decisions – The proposed system will provide users with 
  an intuitive and user-friendly application interface to facilitate data-driven 
  investment decisions, particularly during times when the market is unpredictable 
  or experiencing a downturn. Whereas traditional market analysis tools may not 
  be sufficient to navigate these challenging conditions, the system's advanced 
  machine learning algorithms will provide investors with the insights and guidance 
  they need to make informed and wise decisions. This will help to promote 
  confidence and stability in the market, even during times of uncertainty.
  \subitem 3.	A platform for accessible stock market investment – 
  The proposed system will provide all investors, regardless of their 
  investment knowledge, educational attainment, and societal status, 
  with a platform for participating in the stock market. By offering a 
  simplified yet accurate model for investment decision making, the 
  system will empower users to make informed decisions and invest with confidence. 
  This will help to democratize access to the stock market and promote financial 
  inclusion for all Filipinos.
  \item[(b)] The development of the alamAPI, specifically the Stock Market Price 
  Trend Forecasting System (SMPTF Sys), will provide the following benefits 
  to the future developers or researchers:
  \subitem 1.	Extension of functionality to other financial markets 
  – The proposed system can be easily adapted or expanded to address 
  related problems in other financial markets, such as investing in
  government bonds or personal finance management. 
  This flexibility and versatility will make the system a valuable tool 
  for a wide range of investment and financial management scenarios.
  \subitem 2.	Testing of new trading algorithms and machine learning models – 
  The system provides a platform for introducing and testing new data-driven 
  trading algorithms and machine learning models. This will allow researchers 
  and developers to continually improve the system and keep it at the forefront 
  of data-driven investing technology.
  \subitem 3.	Development of a graphical user interface – 
  To further improve the public accessibility of the system, 
  a user-friendly graphical user interface can be developed as a 
  web or mobile application. This will make the system easy to use 
  and intuitive for all users, regardless of their technical expertise.
  \item[(c)] The development of the alamAPI will help to stimulate economic 
  recovery and development in the country by increasing the number of local 
  investors. As discussed in previous sections, the benefits of the system 
  will encourage more people to invest in the stock market, leading 
  to a multiplier effect that will benefit the economy in several ways. 
  For example, the increased participation in the market will lead to the 
  creation of jobs and a lowering of unemployment rates. Additionally, 
  the influx of capital into the market will drive fast developments and 
  innovations in various industries, and the increased consumer spending 
  that results from successful investing will stimulate economic growth. 
  Overall, the development of the alamAPI will have a positive and 
  far-reaching impact on the economy of the Philippines.
\end{itemize}