\begin{abstract}
    Investing in the stock market can provide significant benefits to both individuals and the economy as a whole. 
    Many people, however, are hesitant to participate due to the high risk involved. This problem is worsened 
    by a lack of access to accurate and reliable stock market information, which is frequently reserved for those 
    who can afford expensive research. Which, when compared to larger private institutions, 
    there is a gap in information available to the public, creating an unfair advantage in the investing market.
    As such, the objective of this study was to develop alamSYS, a system that could collect and process 
    stock market data in order to provide comprehensive stock position suggestions with the utilization of
    DMD-LSTM model and ALMACD. In addition, alamAPP, which showcases the main functionalities of the alamSYS, 
    was also developed. Wherein, the results show that alamSYS, with its efficient and robust components, 
    together with DMD-LSTM predictions along with ALMACD as a trading algorithm, has the potential to 
    provide credible stock trading advice that yields high returns while minimizing potential risks. 
    Moreover, the mobile-based test application's successful integration with external devices demonstrates 
    the system's adaptability and versatility. Ultimately, the socioeconomic impact of alamSYS provide 
    essential advantages to the stock market, individual investors or traders, and the Philippine economy 
    as a whole by bringing about economic growth, increasing investor trust and participation, and limiting 
    potential risks and losses.
    % From 150 to 200 words of short, direct and complete sentences, the abstract 
    % should be informative enough to serve as a substitute for reading the entire SP document 
    % itself.  It states the rationale and the objectives of the research.  
    % In the final Special Problem  document (i.e., the document you'll submit for your final defense), the  abstract should also contain a description of your research results, findings,  and contribution(s).
    
    %  Do not put citations or quotes in the abstract.
    
    % Suggested keywords based on ACM Computing Classification system can be found at \url{https://dl.acm.org/ccs/ccs_flat.cfm}

    \begin{flushleft}
    \begin{tabular}{lp{4.25in}}
    \hspace{-0.5em}\textbf{Keywords:}\hspace{0.25em} & Systems Architecture, Computing Methodologies, Applied Computing, Human-Centered Computing\\
    \end{tabular}
    \end{flushleft}
\end{abstract}
    