\chapter{Review of Related Works and Literature}
\label{chap:lit_review}
Many online stock market analysis tools have recently been available, including: 
(a) Investa Screener; (b) TradingView; (c) Stock Rover; and (d) Investagrams. 
These tools can assist investors in performing fundamental and technical analysis on 
various equities
\cite{Benignos2020, Carey2023, DayTradingz, Investagrams}.
\\

The use of technical analyses, in particular, provides the following 
benefits: (a) the ability to generate profitable buy and sell signals; (b) the performance 
of the technical analysis can be utilized and even show similar performance on different 
markets; (c) can be used to test the significance predictive power of trading rules; and 
(d) provides an easy-to-understand data analysis and visualization tool in conjunction 
with fundamental stock analysis
\cite{Abbad2014AdvantagesOU, Priatmojo2022TechnicalAT, Ausloos_2002, Tangsripairoj2020StockifyAW}.
\\

However, the studies cited above show the following limitations to using 
traditional stock market analysis techniques through the use of online tools: 
(a) the amount of data becomes overwhelming, especially for new investors/traders; 
(b) relying on fundamental and technical analysis alone may lead to missed 
opportunities or incorrect market decisions; and (c) these tools and techniques 
do not eliminate emotional trading.
\\

In recent years, 'artificial intelligence' (AI) has grown in popularity as a tool 
for nearly every endeavor. Particularly in recent years, machine learning techniques 
are increasingly being utilized in the stock market, specifically for: 
(a) stock price predictions; (b) stock movement/trend prediction; and 
(c) stock portfolio management
\cite{Kumbure2022, Strader2020, Soni2022, Rea2020, Guo2022, Budiharto2021}. 

Moreover, there are currently no machine learning-based technologies accessible in the 
Philippines, which according to studies aid to: (a) improve decision accuracy and efficiency; 
(b) increase risk management; and (c) improve trader performance in the short term
\cite{Lu2022MachineLI, Shaheen2020UseOM, Singh_2022, Prasad2021ImportanceOM, 
Zhang2022ApplicationOB, Obthong2020}. In comparison, a number of studies in other nations have 
produced machine learning models for stock market forecasting, some of which are as follows:
\\

The study of \citeA{Mann2015} in the utilization of DMD for financial stock market 
prediction has become the foundation of the study by \citeA{Savas2017} 
on the algorithmic trading strategies with Dynamic Mode Decomposition 
for the Turkish Stock Market. Wherein, based on their results they found out 
that the timing of DMD analysis was not significantly accurate, as such they 
have used a simple moving average with genetic algorithm to improve the market 
timing of DMD, which prevents 80\% of the false trade signals.
\\

In the study by \citeA{Cui2016}, they have found that DMD was able to capture the 
dynamic patterns of the Chinese Stock Market, especially in a sideway trending market.
\citeA{Fraz2022ModelingAF}, researchers from Pakistan and China, was able to 
create a model for the KSE-100 and SSE-100 utilizing machine learning techniques, the GARCH 
family, and non-linear regime-switching models. Based on Akaike's Information Criteria (AIC) 
and Bayesian Information Criteria (BIC), their findings revealed that the standard GARCH model 
is the best-fitted model, and that the LSTM model outperforms the other models in predicting 
the SSE-100.
\\

More recently, \citeA{Sarangi2023ComputingSM}, researchers from India were able 
to perform and analyze the activity of the Bombay Stock Exchange (BSE) using three machine learning models: 
linear regression, polynomial regression, and support vector regression.
\\

These studies demonstrate how widely machine learning models are used in the stock market. 
However, it also demonstrates some limitations of the models, such as: (a) these studies 
are focused outside of the Philippines, so the model developed may not apply directly or 
well to the Philippine Stock Exchange; (b) as the study of \citeA{Shaheen2020UseOM} suggests, the results 
of these models may not necessarily apply to systems in the real world, where the models 
may be unable to adapt to other situations and conditions; 
(c) the utilization of these tools has its limitations. First, these tools
are only based on the past market data, and may not be able to take account
for other events and technical aspects, that can affect the stock market
\cite{Concoda2020}; and (d) most of these tools are closed off to the public, or often behind a 
payment or subscription walls, limiting the resources available for them.
Lastly, there are no existing integrations of these developed machine learning
models with other traditional stock market analysis tools, making them somewhat
ineffective when utilized in a real-world scenario
\cite{CHHAJER2022100015, zou2023stock}.
\\

These points are essential to take note, since investing in the stock market brings 
significant financial benefits to individuals such as: 
(a) it helps alleviate the effects of inflation over time. Whereas, it was noted 
that the Philippines' inflation rate as of April 2023 was 6.6\% \cite{NEDA2023}, 
while savings account  deposit interest rates are only 1-3\% annually \cite{BSP19}. 
Meaning, savings in deposit banks may not keep pace with inflation, 
potentially reducing an individual's purchasing power over time \cite{RBC, EdwardJones}; 
and (b) investing in the stock market can provide individuals with the opportunity for 
significant capital growth without the need for direct investment involvement in 
business operations \cite{USSecAndExComm}.
\\

Also, the stock market is widely acknowledged to play an important role in economic 
growth because it allocates and provides capital to businesses, which drives economic 
activity and growth. This is evident from the fact that stock market performance 
is frequently correlated with the gross domestic product (GDP) of the country
\cite{TradeBrains, Hall2022, Bae2017}.
Furthermore, historical stock price trends can provide insight 
into broader economic movements
\cite{Campbell2021}.
\\

In a study conducted by \citeA{Balaba2017}, they discovered that the stock market
has a positive impact on the Philippines' economy. The study's findings showed that
as the stock market rose, the unemployment rate fell. This is because the performance 
of the stock market leads to job creation, which in turn leads to economic growth.
This, in turn, drives economic growth. This relationship was observed
in the Philippines from 2007 to 2017.
\\

Overall, this review of the related literature and studies, shows that one of the issues 
confronting investors in the Philippine Stock Exchange is the scarcity of resources and 
instruments for making market decisions. Other countries, on the other hand, have begun to 
adopt machine learning techniques for stock market prediction and analysis, allowing for 
more accurate decision-making and lowering the chance of poor investment outcomes. 
However, using these machine learning models does not guarantee profitable market decisions in 
the actual world. As a result, alamSYS was created, with the goal of implementing a deep 
learning model for the Philippine Stock Exchange and deploying this model for use in the 
real world, accessible through a web-based API.
\\

