\subsection{Chronological Utilization of DMD in the Financial Markets}
\label{subsec:chronological_utilization_dmd}
In \citeyear{Mann2015} Mann and Kutz proved that DMD can be used as data-driven analytics 
on the financial market data. Wherein, DMD allows a predictive assessment of 
the market dynamics, which helps in the capitalization of stock market 
strategies and decisions to be applied.

% SUBSECTIONS
\subsubsection{Utilization of DMD for Determining the Cyclic Behavior in the Stock Market (2016)}
\label{subsubsec:dmd_cyclic_behavior}
By utilizing the reproducible Koopman modes it made it possible to have extracted 
four cyclic variations (also reproducible modes) in the stock market, which 
were previously unknown and have persisted since the 1870s’ 
global economic crisis
\cite{Hua2016,Williamson2015}.
\subsubsection{Utilization of DMD as part of an Algorithmic Trading Strategies for the Turkish Stock Market (2015 and 2017)}
\label{subsubsec:dmd_algorithmic_trading}
The study of \citeA{Mann2015} in the utilization of DMD for financial stock market 
prediction has become the foundation of the study by \citeA{Savas2017} 
on the algorithmic trading strategies with Dynamic Mode Decomposition 
for the Turkish Stock Market. Wherein, based on their results they found out 
that the timing of DMD analysis was not significantly accurate, as such they 
have used a simple moving average with genetic algorithm to improve the market 
timing of DMD, which prevents 80\% of the false trade signals.
\vspace{0.5cm}
\\Furthermore, this also shows that DMD is an effective alpha 
model that is easy to implement and use for any algorithmic trading 
strategy, and the addition of technical analysis tools can further improve 
its capabilities, especially on the predictive temporal side of the data.
\subsubsection{Utilization of DMD-based Trading Strategy in the Chinese Stock Market (2016)}
\label{subsubsec:dmd_chinese_stock_market}
In the study by \citeA{Cui2016}, they have found that DMD was able to capture the 
dynamic patterns of the Chinese Stock Market, especially in a sideway trending market.
\vspace{0.5cm}
\\Their study also shows that the predictive ability of DMD can effectively 
model the behavior of the Chinese Stock Market, even if there are no 
clear trends that can be observed.
\subsubsection{Utilization of Adaptive Elastic DMD to Improve Momentum Strategies (2021)}
\label{subsubsec:dmd_adaptive_elastic}
A study by \citeA{Uchiyama2021}, using Adaptive Elastic Dynamic Mode Decomposition 
(AEDMD) shows that they were able to estimate the market trend, and were able to 
demonstrate that the approach is better than existing momentum strategy which 
are only based on simple past trends.