% Utilization of Machine Learning in Stock Market Trading
\subsection{Utilization of Machine Learning in Stock Market Trading}
In recent years, there has been a surge in interest in the use of machine learning.
Learning techniques for predicting stock market movement in the short and long term. 
As a result, numerous studies and practical applications investigating the use of 
machine learning in stock market prediction have been conducted. These efforts aim 
to improve prediction accuracy and assist investors in making informed decisions
\cite{Kumbure2022, Strader2020, Soni2022, Rea2020, Guo2022}.
In this regard, one of the common techniques used is the Long Short-Term Memory (LSTM).
LSTM is a deep learning model that is widely used to forecast the stock market. 
A study by \citeA{Budiharto2021} found that LSTM was effective in predicting the 
Indonesian stock market with 95\% accuracy using a short-term data. 
Which suggests that LSTM can be a useful tool for making short-term 
stock market forecasts.
\hfill \\

The use of Dynamic Mode Decomposition (DMD) for predicting stock market price 
trends has recently gained traction in the financial industry. DMD is a mathematical 
method for identifying patterns and trends in large data sets, such as stock market 
data. It is possible to make more accurate predictions about future stock price 
movements by applying DMD to stock market data. This can help investors make more 
informed investment decisions and potentially generate higher returns.
However, a study by \citeA{Lu2020} found that DMD is faster than 
Proper Orthogonal Decomposition, but it is less accurate.
\hfill \\

Other studies have shown that DMD can be effectively applied to the Turkish and 
Indian stock markets to predict market price trends
\cite{Savas2017, Kuttichira2017}.
These studies show that DMD is simple to implement and can be used 
as a useful enhancer for making stock market predictions.
\hfill \\